---
title: "IS606 - Final Meetup"
author: Jason Bryer, Ph.D.
date: December 17, 2015
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
---
	
<div class="notes">
Documentation on using ioslides is available here:
http://rmarkdown.rstudio.com/ioslides_presentation_format.html
Some slides are adopted (or copied) from OpenIntro: https://www.openintro.org/
</div>

```{r setup, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
set.seed(2112)
library(ggplot2)
library(openintro)
library(IS606)
library(reshape2)
library(psych)
library(reshape2)
library(xtable)
options(width=100)
par(mar=c(2.5,1,2,1))

```

## Final Exam

```{r}
options(digits=3)
data1 <- data.frame(x=c(10,8,13,9,11,14,6,4,12,7,5),
					y=c(8.04,6.95,7.58,8.81,8.33,9.96,7.24,4.26,10.84,4.82,5.68))
data2 <- data.frame(x=c(10,8,13,9,11,14,6,4,12,7,5),
					y=c(9.14,8.14,8.74,8.77,9.26,8.1,6.13,3.1,9.13,7.26,4.74))
data3 <- data.frame(x=c(10,8,13,9,11,14,6,4,12,7,5),
					y=c(7.46,6.77,12.74,7.11,7.81,8.84,6.08,5.39,8.15,6.42,5.73))
data4 <- data.frame(x=c(8,8,8,8,8,8,8,19,8,8,8),
					y=c(6.58,5.76,7.71,8.84,8.47,7.04,5.25,12.5,5.56,7.91,6.89))

desc <- data.frame(
	Mean.x = c(mean(data1$x), mean(data2$x), mean(data3$x), mean(data4$x)),
	Mean.y = c(mean(data1$y), mean(data2$y), mean(data3$y), mean(data4$y)),
	Median.x = c(median(data1$x), median(data2$x), median(data3$x), median(data4$x)),
	Median.y = c(median(data1$y), median(data2$y), median(data3$y), median(data4$y)),
	SD.x = c(sd(data1$x), sd(data2$x), sd(data3$x), sd(data4$x)),
	SD.y = c(sd(data1$y), sd(data2$y), sd(data3$y), sd(data4$y))
)
desc
```

## Correlations

```{r}
cor(data1$x, data1$y)
cor(data2$x, data2$y)
cor(data3$x, data3$y)
cor(data4$x, data4$y)
```

## Linear Regressions

```{r}
lm(y ~ x, data=data1)$coefficients
lm(y ~ x, data=data2)$coefficients
lm(y ~ x, data=data3)$coefficients
lm(y ~ x, data=data4)$coefficients
```

## Scatter Plots {.flexbox .vcenter}

```{r}
par.orig <- par(mfrow=c(2,2))
plot(data1$x, data1$y); plot(data2$x, data2$y); plot(data3$x, data3$y); plot(data4$x, data4$y)
par(par.orig)
```

## Anscombe's Quartet

Data sets constructed by Fancis Anscombe in 1973 to demonstrate:

* The importance of visualizing data.
* The role of outliers on descriptive statistics.


See more on Wikipedia: https://en.wikipedia.org/wiki/Anscombe%27s_quartet

Generating Data with Identical Statistics but Dissimilar Graphics: http://www.tandfonline.com/doi/abs/10.1198/000313007X220057

## My Work

My research interest is in propensity score methods. Propensity score analysis (PSA) is a quasi-experimental design used to estimate causality from observational studies. It is generally conducted in two phases:

1. Estimate propensity scores (i.e. probability of being in the treatment) using the observed covariates.
	a. Check balance
	b. Re-estimate propensity scores
2. Estimate effect sizes using typical group differences (e.g. t-tests)

Areas I have worked on:

* Multilevel PSA (see [`multilevelPSA`](http://jason.bryer.org/multilevelPSA) R package)
* Matching with non-binary treatments (see [`TriMatch`](http://jason.bryer.org/TriMatch) R package)
* Bootstrapping PSA (see [`PSAboot`](http://jason.bryer.org/PSAboot) R package)

## Thank You

This has been a great semester. Please don't hesitate to reach out:

* Email: jason.bryer@gmail.com
* Github: http://github.com/jbryer
* Blog: http://bryer.org
* [LinkedIn](https://www.linkedin.com/profile/view?id=AAMAAATGdnoBOWXg80yqna6fSkgnZdabZP7Ck9w&trk=hp-identity-name)
* Twitter: [@jbryer](https://twitter.com/jbryer) (don't Tweet very much though)


