---
title: "Mathematics Anxiety Scale Results"
runtime: shiny
---


```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source('config.R')

surveyId <- 'SV_0If2SzYPhQvEBRb' # MASS only
# responseId <- 'R_1IblE2Oi6Hzjm0a' # For testing SASR only

results.filename <- 'mass-results.rda'

mass.levels <- c('Strongly Agree', 'Agree', 'Neither Agree nor Disagree', 
                 'Disagree', 'Strongly Disagree')

mass.items <- c('I find math interesting.',
                'I get uptight during math tests.',
                'I think that I will use math in the future.',
                'Mind goes blank and I am unable to think clearly when doing my math test.',
                'Math relates to my life.',
                'I worry about my ability to solve math problems.',
                'I get a sinking feeling when I try to do math problems.',
                'I find math challenging.',
                'Mathematics makes me feel nervous.',
                'I would like to take more math classes.',
                'Mathematics makes me feel uneasy.',
                'Math is one of my favorite subjects.',
                'I enjoy learning with mathematics.',
                'Mathematics makes me feel confused.')
mass.reverse <- c(TRUE,FALSE,TRUE,TRUE,TRUE,TRUE,FALSE,TRUE,FALSE,FALSE,
                  TRUE,FALSE,FALSE,TRUE)

library(qualtrics)
library(ggplot2)
library(reshape2)
library(likert)

# Student data
if(file.exists(results.filename)) {
  load(results.filename)
  student.mass <- sasr[sasr$ResponseID == responseId,]
} else {
  student.mass <- data.frame()
}

# Keep a cache of the SASR Qualtrics results
if(nrow(student.mass) == 0) {
	sasr <- getSurveyResults(user, pass, surveyId)
	save(sasr, file=results.filename)
	student.mass <- sasr[sasr$ResponseID == responseId,]
}

```

```{r MASS, eval=TRUE, echo=FALSE, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
mass.results <- student.mass[,11:24]
names(mass.results) <- mass.items
for(i in seq_len(ncol(mass.results))) {
	mass.results[,i] <- factor(mass.results[,i], levels=1:5, labels=mass.levels, ordered=TRUE)
}

mass.results$ID <- 1
tmp <- melt(mass.results, id.vars='ID', stringsAsFactors=FALSE)
tmp$ID <- NULL
names(tmp) <- c('Item','Response')
tmp$xend <- 6
tmp$Item <- as.character(tmp$Item)
tmp$Response <- factor(tmp$Response, levels=mass.levels, ordered=TRUE)

tmp$reverse <- mass.reverse
if(sum(tmp$reverse) > 0) {
	tmp[tmp$reverse,]$xend <- 0
	tmp[tmp$reverse,]$Item <- paste0(tmp[tmp$reverse,]$Item, '\n(reverse scored)')
}
tmp$value <- abs(as.integer(tmp$Response) - tmp$xend)
tmp$hjust <- ifelse(tmp$reverse, -2, 3)

tmp$ItemWrap <- likert:::label_wrap_mod(tmp$Item, width=60)

cbind(mass.items, mass.reverse, as.integer(mass.results[1:14]))

# Strongly disagree = 5
mass.scored <- as.integer(mass.results[1:14])
mass.scored[mass.reverse] <- 6 - mass.scored[mass.reverse]
mass.score <- 5 - (sum(mass.scored) / 14)
mass.feedback <- ''

if(mass.score <= 1.9) {
	mass.feedback <- 'comfortably low math anxiety'
} else if(mass.score <= 2.5) {
	mass.feedback <- 'normal or average math anxiety'
} else if(mass.score <= 3.5) {
	mass.feedback <- 'moderately high math anxiety'
} else if(mass.score <=3.9) {
	mass.feedback <- 'high math anxiety'
} else {
	mass.feedback <- 'extremely high math anxiety'
}

```

Your total score on the math anxiety section was `r prettyNum(mass.score, digits=2)` (score range is 0 to 4) which indicates that you have `r mass.feedback`.

```{r MASS-figure, eval=TRUE, echo=FALSE, results='hide', message=FALSE, warning=FALSE, fig.width=12, fig.height=5}
ggplot(tmp, aes(x=as.integer(Response), y=Item, color=value)) +
		geom_segment(aes(xend=xend, yend=Item)) +
		geom_point(size=5) +
		geom_text(aes(label=value, hjust=hjust), size=4) +
		theme(axis.ticks.x=element_blank(), legend.position='none') +
		ylab('') + xlab('') +
		scale_x_continuous(limits=c(0,6), breaks=1:5, labels=(gsub(' ', '\n', mass.levels))) + 
		scale_color_continuous(limits=c(1,6), low='#FF9900', high='#660066')

```


##### References

Bai, H., Wang, L., Pan, W., Frey, M. (2009). Measuring mathematics anxiety: psychometric analysis of a bidimensional affective scale. *Journal of Instructional Psychology, 36*(3). Retrieved from http://www.freepatentsonline.com/article/Journal-Instructional-Psychology/211235540.html

Betz, N. E. (1978). Prevalence, distribution, and correlates of math anxiety in college students. *Journal of Counseling Psychology, 25*(5), 441-448.
